Accuracy and precision of zero-heat-flux temperature monitoring

### 2019-12-09 manuscript/manuscript.Rmd
additional formatting requested anesthesiology

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring"
subtitle: A systematic review and meta-analysis
description: "A systematic review and meta-analysis"
# author:
# - name: Aaron Conway
#   affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   email: aaron.conway@utoronto.ca
#   url: https://www.aaronconway.info
# - name: Megan Bittner
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
# - name: Dan Phan
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
# - name: Navpreet Kamboj
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   email: navpreet.kamboj@mail.utoronto.ca
# - name: Kristina Chang
#   affiliation: Toronto General Hospital, UHN
# - name: Elizabeth Tipton
#   affiliation: Department of Statistics, Northwestern University
# - name: Matteo Parotto
#   affiliation: Toronto General Hospital, UHN
# date: "`r Sys.Date()`"
# repository_url: https://github.com/awconway/zhf-review
# twitter:
#   creator: "@aw_conway"
# output: distill::distill_article
bibliography: Extras/bibliography.bib
csl: Extras/anesthesiology.csl
author:
  - Aaron Conway PhD:
      email: aaron.conway@utoronto.ca
      phone: +1 416 946 7112
      address: 585 University Ave, 4NU - 476 | Toronto, ON  M5G 2N2
      institute: [PMCC, LBFON, QUT]
      correspondence: true
  - Megan Bittner BSc:
      institute: [LBFON]
      correspondence: false
  - Dan Phan BSc:
      institute: [LBFON]
      correspondence: false
  - Kristina Chang MScN:
      institute: [PMCC]
      correspondence: false
  - Navpreet Kamboj BScN:
      institute: [LBFON]
      correspondence: false
  - Elizabeth Tipton PhD:
      institute: [NW]
      correspondence: false
  - Matteo Parotto MD, PhD:
      institute: [TGH, UoT]
      correspondence: false
institute:
  - PMCC: Peter Munk Cardiac Centre, University Health Network, Toronto, Canada
  - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto, Toronto, Canada
  - QUT: School of Nursing, Queensland University of Technology (QUT), Brisbane, Australia
  - NW: Department of Statistics, Northwestern University, Evanston, IL, United States
  - TGH: Department of Anesthesia and Pain Management, Toronto General Hospital, UHN, Toronto, Canada
  - UoT: Department of Anesthesia and Interdepartmental Division of Critical Care Medicine, University of Toronto, Toronto, Canada
output:
  bookdown::word_document2:
    reference_docx: Extras/manuscript_template.docx
    pandoc_args:
      - --lua-filter=Extras/scholarly-metadata.lua
      - --lua-filter=Extras/author-info-blocks.lua
      - --lua-filter=Extras/pagebreak.lua
always_allow_html: true
params:
  distill: FALSE
  word: TRUE
---

>>>>

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring"
subtitle: A systematic review and meta-analysis
description: "A systematic review and meta-analysis"
# author:
# - name: Aaron Conway
#   affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   email: aaron.conway@utoronto.ca
#   url: https://www.aaronconway.info
# - name: Megan Bittner
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
# - name: Dan Phan
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
# - name: Navpreet Kamboj
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   email: navpreet.kamboj@mail.utoronto.ca
# - name: Kristina Chang
#   affiliation: Toronto General Hospital, UHN
# - name: Elizabeth Tipton
#   affiliation: Department of Statistics, Northwestern University
# - name: Matteo Parotto
#   affiliation: Toronto General Hospital, UHN
# date: "`r Sys.Date()`"
# repository_url: https://github.com/awconway/zhf-review
# twitter:
#   creator: "@aw_conway"
# output: distill::distill_article
bibliography: Extras/bibliography.bib
csl: Extras/anesthesiology.csl
author:
  - Aaron Conway PhD:
      email: aaron.conway@utoronto.ca
      phone: +1 416 946 7112
      address: 585 University Ave | Toronto, ON  M5G 2N2
      institute: [PMCC, LBFON, QUT]
      correspondence: true
  - Megan Bittner BSc:
      institute: [LBFON]
      correspondence: false
  - Dan Phan BSc:
      institute: [LBFON]
      correspondence: false
  - Kristina Chang MScN:
      institute: [PMCC]
      correspondence: false
  - Navpreet Kamboj BScN:
      institute: [LBFON]
      correspondence: false
  - Elizabeth Tipton PhD:
      institute: [NW]
      correspondence: false
  - Matteo Parotto MD, PhD:
      institute: [TGH, UoT]
      correspondence: false
institute:
  - PMCC: Peter Munk Cardiac Centre, University Health Network, Toronto, Canada
  - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto, Toronto, Canada
  - QUT: School of Nursing, Queensland University of Technology (QUT), Brisbane, Australia
  - NW: Department of Statistics, Northwestern University, Evanston, IL, United States
  - TGH: Department of Anesthesia and Pain Management, Toronto General Hospital, UHN, Toronto, Canada
  - UoT: Department of Anesthesia and Interdepartmental Division of Critical Care Medicine, University of Toronto, Toronto, Canada
output:
  bookdown::word_document2:
    reference_docx: Extras/manuscript_template.docx
    pandoc_args:
      - --lua-filter=Extras/scholarly-metadata.lua
      - --lua-filter=Extras/author-info-blocks.lua
always_allow_html: true
params:
  distill: FALSE
  word: TRUE
---
